Plots_manuscript_G_BLUP

### 2020-09-30 R/Plots_manuscript_G_BLUP.Rmd
Start comparisons of GWAS and QTL intervals with FT annotations

---
title: "Plots_manuscript_v0.3"
author: "Alice MacQueen"
date: "7/22/2020"
output: html_document
---

Add any libraries/scripts that need to be loaded for these analyses here.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cowplot)
library(viridis)
library(lubridate)
library(switchgrassGWAS)
library(GGally)
library(maps)
library(ggmap)
usa <- map_data("usa")
source("~/Github/Functions_ggplot-theme-adjustments_2018-01-03.R")
```

# Load data
Add any data that needs to be loaded for these analyses here.
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
subpops <- read_rds(file.path(workingdir, "data", "subpop_color_coding.rds"))
phe_gr_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_GR50.rds"))
phe_fl_df <- read_rds(file.path(workingdir, "data",
                                "Weather_related_phe_for_asreml_h2_FL50.rds"))
phenotypes <- readRDS("~/Github/pvdiv-phenology-gxe/data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
h2gr <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "h2_df_GR50_related_functions_of_weather_v1.csv"))
h2fl <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "h2_df_FL50_related_functions_of_weather_v1.csv"))
h2gr_gxe <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "gxe_and_h2_df_GR50_related_functions_of_weather_v1.csv"))
h2fl_gxe <- read_csv(file.path(workingdir, "analysis", "heritability", "kinship_subpop", "gxe_and_h2_df_FL50_related_functions_of_weather_v1.csv"))

h2gr <- h2gr %>%
  full_join(h2gr_gxe)
h2fl <- h2fl %>%
  full_join(h2fl_gxe)
```
as well as the code for any new analyses that I'm running to do new writeup for the manuscript v0.3.

v0.2 has the ASReml h2 analysis, has BLUPs for G (which as of v0.3 probably needs a GxE term... define some possibilities below.)

Results: h2 at single sites. Then h2 at all eight sites. And so there must be GxE, and there must be a lot of rank-changing GxE, in that we can’t predict ranks across sites.

To show this, make barplots of the different variables and facet them by site. Then, show heritability across all eight sites (in a model with a random effect of site, interacted with some number of eigenvectors from a SVD of the kinship matrix.)

# Map Fig 1A

```{r}
subpops
library(ggrepel)

metaplot <- metadata %>%
  filter(SUBPOP %in% c("Gulf", "Midwest") & !is.na(LATITUDE)) %>%
  mutate(LONGITUDE = -LONGITUDE)
metaplot$ECOTYPE_NNET <- factor(metaplot$ECOTYPE_NNET, levels = c("Coastal", "Lowland", "Upland", "Unknown"))
siteplot <- sites %>%
  filter(!(SITE %in% c("FRMI", "OVTN")))

ggplot() + 
  geom_polygon(data = usa, aes(x=long, y = lat, group = group), 
               fill = "white", color = "black") +
  coord_quickmap(xlim = c(-105, -66), ylim = c(25, 50)) +
  geom_jitter(data = metaplot, aes(x = LONGITUDE, y = LATITUDE, 
                                   color = SUBPOP, shape = ECOTYPE_NNET),
              width = 0.45, height = 0.45) + 
  geom_point(data = siteplot, aes(x = Longitude, y = Latitude), shape = 21, size = 4, stroke = 1.5, fill = "white") +
  geom_point(data = siteplot, aes(x = Longitude, y = Latitude), shape = 4, size = 3, stroke = 1.5) +
  geom_label_repel(data = siteplot, aes(x = Longitude, y = Latitude, label = manu_site), alpha = 0.7) +
  labs(x = "Longitude", y = "Latitude") + 
  theme(legend.position = "right") +
  scale_color_manual(values = c("#F47F72", "#442C83")) +
  scale_shape_manual(values = c(0, 6, 1, 4)) 
  #scale_fill_manual(values = c("#280B54FF","#FAC127FF", "#D44842FF", "white")) +
  #scale_color_manual(values = c(rep("black", 10), "#280B54FF","#FAC127FF", "#D44842FF", "white", "#280B54FF","#FAC127FF", "#D44842FF", "white"), guide = FALSE) +
  #scale_alpha_manual(values = c(0.7, 0.7, 0.7, 0.7), guide = FALSE)
save_plot(filename = "../manuscript/plots/Map_subpops_and_Ecotypes.png", plot = last_plot(), base_height = 3)
?geom_point
```

# -- Figure 1 B
# Phenotype correlations
can you easily look at the correlation between greenup ranks at OK versus NE?
```{r}
phe_gr_df %>%
  filter(SITE %in% c("LINC", "STIL")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = LINC)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

phe_gr_df %>%
  filter(SITE %in% c("STIL", "PKLE")) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, -PLOT_GL) %>%
  pivot_wider(names_from = "SITE", values_from = "GR50", values_fn = mean) %>%
  ggplot(aes(x = STIL, y = Lat_origin)) +
  geom_hex() + #aes(color = SUBPOP), height = 1, width = 1) +
  scale_fill_viridis(option = "B",
                     end = 0.9, direction = -1)

cor_gr <- phe_gr_df %>%
  left_join(select(sites, SITE, manu_site)) %>%
  ungroup() %>%
  select(PLANT_ID:GR50, manu_site, -PLOT_GL, -SITE) %>%
  pivot_wider(names_from = "manu_site", values_from = "GR50", values_fn = mean)
cor_fl <- phe_fl_df %>%
  left_join(select(sites, SITE, manu_site)) %>%
  ungroup() %>%
  select(PLANT_ID:FL50, manu_site, -PLOT_GL, -SITE) %>%
  pivot_wider(names_from = "manu_site", values_from = "FL50", values_fn = mean)

cor_north <- phe_gr_df %>%
  left_join(select(sites, SITE, manu_site)) %>%
  ungroup() %>%
  filter(Lat_origin > 40) %>%
  select(PLANT_ID:GR50, manu_site, -PLOT_GL, -SITE) %>%
  pivot_wider(names_from = "manu_site", values_from = "GR50", values_fn = mean)
cor_south <- phe_gr_df %>%
  left_join(select(sites, SITE, manu_site)) %>%
  ungroup() %>%
  filter(Lat_origin < 32) %>%
  select(PLANT_ID:GR50, manu_site, -PLOT_GL, -SITE) %>%
  pivot_wider(names_from = "manu_site", values_from = "GR50", values_fn = mean)
cor(cor_north[,5:13], use = "pairwise") %>%
  switchgrassGWAS:::reorder_cormat(.) %>%
  ggcorr(data = NULL, cor_matrix = ., label = TRUE)
cor(cor_south[,5:13], use = "pairwise") %>%
  switchgrassGWAS:::reorder_cormat(.) %>%
  ggcorr(data = NULL, cor_matrix = ., label = TRUE)

cor(cor_gr$STIL, cor_gr$LINC, use = "pairwise")
cor(cor_gr[,5:13], use = "pairwise") %>%
  ggcorr(data = NULL, cor_matrix = ., label = TRUE)
cor(cor_fl[,5:13], use = "pairwise") %>%
  ggcorr(data = NULL, cor_matrix = ., label = TRUE)

# two different ways. Think I like the second more. Force latitudinal order.
cor_gr %>%
  filter(SUBPOP %in% c("Midwest", "Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  cor(use = "pairwise") %>%
  switchgrassGWAS:::reorder_cormat(.) %>%
  ggcorr(data = NULL, cor_matrix = ., label = TRUE)
```

```{r}
pand <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pane <- cor_fl %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panf <- cor_fl %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
pana <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = c(0.4, 0.85))
panb <- cor_gr %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")
panc <- cor_gr %>%
  filter(SUBPOP %in% c("Gulf", "Midwest")) %>%
  select(TX1, TX2, TX3, OK, MO, NE, MI, SD) %>%
  ggcorr(method = "pairwise", label = FALSE, layout.exp = 0.2, hjust = 0.95) +
  scale_fill_gradientn(colors = c("#440154FF", "#3B528BFF", "#2C728EFF",
                                      "white", "#27AD81FF", "#5DC863FF",
                                      "#FDE725FF"), limits = c(-1,1)) +
  theme(legend.position = "none")

pheno_corr <- plot_grid(pana, panb, panc, pand, pane, panf, nrow = 2)
save_plot(filename = "../manuscript/plots/Phenotypic_correlations_GR50_FL50_2.svg", plot = pheno_corr, base_width = 6.5)
```

# --- Fig 1 C & D
# Heritability Plots

Within common gardens, h2 were typically quite high: 62% on average for greenup date, and 87% for flowering date. However, h2 were not consistently high, notably for greenup at our OK and NE common gardens.
```{r}
h2all <- h2fl %>%
  full_join(h2gr)

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD")) %>%
  group_by(phe) %>%
  summarise(meanh2 = mean(Estimate))

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD")) %>%
  filter(Estimate < 0.2)

h2all %>%
  filter(phe %in% c("FL50", "GR50") & site %in% c("eight_sites")) %>%
  group_by(phe) %>%
  summarise(meanh2 = mean(Estimate))

h2all %>%
  filter(phe %in% c("GR50") & site %in% c("tx_sites", "north_sites")) %>%
  mutate(GandGxE = Estimate + GxE_Estimate) %>%
  select(GandGxE, Estimate:phe, GxE_Estimate) %>%
  group_by(site) %>%
  summarise(meanh2 = mean(Estimate + GxE_Estimate))

h2all %>%
  filter(site %in% c("eight_sites")) %>%
  mutate(GandGxE = Estimate + GxE_Estimate)  %>%
  select(GandGxE, site:phe, Estimate, SE, GxE_Estimate, GxE_SE)
```

## h2 as functions of GR50 and FL50
```{r}
h2all <- h2fl %>%
  full_join(h2gr)
unique(h2all$site)
f1h2 <- h2all %>%
  filter(phe %in% c("FL50", "GR50")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              TRUE ~ phe))
f1h2$site <- factor(f1h2$site, levels = c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All"))#, "Texas", "North"))
f1h2$phe_name <- factor(f1h2$phe_name, levels = c("50% greenup", "50% flowering"))
f1h2$subpop_name <- factor(f1h2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
ggh21 <- f1h2 %>%
  filter(!(site %in% c("nine_sites", "IL")) & !is.na(subpop_name) & !is.na(phe_name) & !is.na(site)) %>%
  ggplot(aes(x = site, y = Estimate)) +
  geom_bar(aes(fill = site %in% c("All", "Texas", "North")), stat = "identity") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(phe_name ~ subpop_name) +
  theme(panel.spacing.x = unit(0.1, 'cm'), 
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "none") + 
  ylim(c(0, 1)) +
  xlab("Common Gardens") + 
  ylab(bquote('h'^2)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
  #
save_plot("../manuscript/plots/h2_GR_FL_site_by_subpop_k_specific.png", plot = ggh21, base_width = 5.5, base_height = 3)
```

## h2 flowering weather
```{r}
flh2 <- h2fl %>%
  filter(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d")) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "all",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "FL50" ~ "50% flowering",
                              phe == "dyln_fl50" ~ "daylength",
                              phe == "dyln_change_sec" ~ "daylength change (s)",
                              phe == "cgdd_12c_gr2fl" ~ "GDD, GR to FL",
                              phe == "crain_gr2fl" ~ "Rainfall, GR to FL",
                              phe == "crain_1d" ~ "Rainfall, 1 day",
                              phe == "crain_2d" ~ "Rainfall, 2d sum",
                              phe == "crain_3d" ~ "Rainfall, 3d sum",
                              phe == "crain_5d" ~ "Rainfall, 5d sum",
                              phe == "crain_7d" ~ "Rainfall, 7d sum",
                              TRUE ~ phe))
flh2$site <- factor(flh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North")))
flh2$phe_name <- factor(flh2$phe_name, levels = c("50% flowering", "daylength",
                                                  "daylength change (s)",
                                                  "GDD, GR to FL",
                                                  "Rainfall, GR to FL",
                                                  "Rainfall, 1 day",
                                                  #"Rainfall, 2d sum",
                                                  "Rainfall, 3d sum",
                                                  "Rainfall, 5d sum"#,
                                                  #"Rainfall, 7d sum"
                                                  ))
flh2$subpop_name <- factor(flh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "all"))
site_plot <- rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "MI", "SD", "All", "Texas", "North"))
subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))

flh2_p1 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)

save_plot("../manuscript/plots/h2_FL_site_weather_functions_single_sites_k_specific.png", plot = flh2_p1, base_height = 7, base_asp = 1.1)

site_plot <- c("All", "Texas", "North")

flh2_p2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.8)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

save_plot("../manuscript/plots/h2_FL_site_weather_functions_site_groups_k_specific.png", plot = flh2_p2, base_height = 4, base_asp = 1.5)

site_plot <- c("All")

flh2_p3 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.5)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_FL_site_weather_functions_All_Sites_k_specific.png", plot = flh2_p3, base_height = 3.5)
```
## gxe flowering all, north, texas
```{r}
site_plot <- c("All", "Texas", "North")

fl_barplot2 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>%
  select(site:phe, subpop_name, phe_name, ends_with("SE")) %>%
  pivot_longer(cols = ends_with("SE"), names_to = "Type", values_to = "SE") %>%
  mutate(type_name = case_when(Type == "SE" ~ "G",
                               Type == "GxE_SE" ~ "GxE",
                               Type == "error_SE" ~ "error",
                               Type == "Env_SE" ~ "E")) %>%
  select(-Type)
fl_barplot <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>%
  select(site:phe, subpop_name, phe_name, ends_with("Estimate")) %>%
  pivot_longer(cols = ends_with("Estimate"), names_to = "Type", values_to = "Estimate") %>%
  mutate(type_name = case_when(Type == "Estimate" ~ "G",
                               Type == "GxE_Estimate" ~ "GxE",
                               Type == "error_Estimate" ~ "error",
                               Type == "Env_Estimate" ~ "E"))
fl_barplot <- fl_barplot %>%
  left_join(fl_barplot2)
fl_barplot$type_name <- factor(fl_barplot$type_name, levels = rev(c("G", "GxE", "E", "error")))

fl_bar_gxe <- fl_barplot %>%
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = type_name)) + 
  geom_errorbar(data = filter(fl_barplot, type_name == "G"), aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  facet_grid(site ~ subpop_name)+
  scale_fill_viridis(discrete = TRUE, direction = -1) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = GxE_Estimate+Estimate), linetype = 2) + xlab("") +
  ylab("Variance Explained")

save_plot("../manuscript/plots/Var_Comp_flowering_site_groups.png", plot = fl_bar_gxe, base_width = 5.5, base_height = 4)

flh2_p4 <- flh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = GxE_Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% flowering")) +
  geom_errorbar(aes(ymin = GxE_Estimate - GxE_SE, ymax = GxE_Estimate + GxE_SE), width = 0.3) +
  geom_linerange(aes(ymin = GxE_Estimate, ymax = GxE_Estimate + GxE_SE)) +
  geom_linerange(aes(ymin = GxE_Estimate - GxE_SE, ymax = GxE_Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(flh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "FL50"), aes(yintercept = GxE_Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")

save_plot("../manuscript/plots/h2_FL_site_weather_functions_site_groups_k_specific.png", plot = flh2_p2, base_height = 4, base_asp = 1.5)

library(scales)
show_col(viridis(4)) # #440154FF   #31688EFF
```

## h2 greenup weather

```{r}
unique(h2gr$site)
grh2 <- h2gr %>%
  filter(!(phe %in% c("FL50", "dyln_fl50", "dyln_change_sec", "cgdd_12c_gr2fl", "crain_gr2fl", "crain_1d", "crain_2d", "crain_3d", "crain_5d", "crain_7d", "DYLN"))) %>%
  mutate(site = case_when(is.na(site) ~ "all",
                          site == "eight_sites" ~ "All",
                          site == "tx_sites" ~ "Texas",
                          site == "north_sites" ~ "North",
                          TRUE ~ site),
         subpop_name = case_when(subpop == "Gulf_and_Midwest" ~ "Gulf and Midwest",
                                 subpop == "three_subpops" ~ "All",
                                 TRUE ~ subpop),
         phe_name = case_when(phe == "GR50" ~ "50% greenup",
                              phe == "FL50" ~ "50% flowering",
                              phe == "cgdd_12c_jan2gr" ~ "GDD 01-01 to GR",
                              phe == "cgdd_8c_jan2gr" ~ "GDD 8C 01-01 to greenup",
                              phe == "tmax_18d" ~ "Max T, 18d mean",
                              phe == "tmin_18d" ~ "Min T, 18d mean",
                              phe == "tave_18d" ~ "Mean T, 18d mean",
                              phe == "tmax_10d" ~ "Max T, 10d mean",
                              phe == "tmin_10d" ~ "Min T, 10d mean",
                              phe == "tave_10d" ~ "Mean T, 10d mean",
                              phe == "tmax_5d" ~ "Max T, 5d mean",
                              phe == "tmin_5d" ~ "Min T, 5d mean",
                              phe == "tave_5d" ~ "Mean T, 5d mean",
                              phe == "cgdd_12c_10d" ~ "GDD, 10d",
                              phe == "cgdd_12c_18d" ~ "GDD, 18d",
                              phe == "cgdd_12c_5d" ~ "GDD, 5d",
                              TRUE ~ phe))
grh2$site <- factor(grh2$site, levels = rev(c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North", "nine_sites")))
grh2$phe_name <- factor(grh2$phe_name, levels = c("50% greenup", "GDD, 5d",
                                                  "Min T, 5d mean",
                                                  #"Mean T, 5d mean",
                                                  #"Max T, 5d mean",
                                                  "GDD, 10d",
                                                  "Min T, 10d mean",
                                                  #"Mean T, 10d mean",
                                                  #"Max T, 10d mean",
                                                  "GDD, 18d",
                                                  "Min T, 18d mean",
                                                  #"Mean T, 18d mean",
                                                  #"Max T, 18d mean",
                                                  #"GDD 8C 01-01 to greenup",
                                                  "GDD 01-01 to GR"))
grh2$subpop_name <- factor(grh2$subpop_name, levels = c("Gulf", "Midwest", "Gulf and Midwest", "Atlantic", "All"))

subpop_v <- list(Gulf = "Gulf", Midwest = "Midwest", Gulf_and_Midwest = c("Gulf", "Midwest"), Atlantic = "Atlantic", three_subpops = c("Atlantic", "Gulf", "Midwest"))

site_plot <- c("TX1", "TX2", "TX3", "OK", "MO", "NE", "IL", "MI", "SD", "All", "Texas", "North")

grh2_p1 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 1.1)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_single_sites_k_specific.png", plot = grh2_p1, base_height = 7.5, base_asp = 1.1)

site_plot <- c( "All", "Texas", "North")

grh2_p2 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.6)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1)
save_plot("../manuscript/plots/h2_GR_site_weather_functions_site_groups_k_specific.png", plot = grh2_p2, base_height = 5, base_asp = 1.3)

site_plot <- c( "All")

grh2_p3 <- grh2 %>%
  filter(subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & !is.na(phe_name)) %>% # subpop == subpop_v[[i]] & 
  ggplot(aes(x = phe_name, y = Estimate)) +
  geom_bar(stat = "identity", aes(fill = phe_name == "50% greenup")) +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.3) +
  geom_linerange(aes(ymin = Estimate, ymax = Estimate + SE)) +
  geom_linerange(aes(ymin = Estimate - SE, ymax = Estimate)) +
  facet_grid(site ~ subpop_name) +
  geom_hline(data = filter(grh2, subpop_name %in% c("Gulf and Midwest", subpop_v[[1]], subpop_v[[2]]) & (site %in% site_plot) & !is.na(site) & phe == "GR50"), aes(yintercept = Estimate), linetype = 2) +
  theme(panel.spacing.x = unit(0.1, 'cm'), axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), legend.position = "none") + ylim(c(0, 0.11)) +
  scale_fill_viridis(discrete = TRUE, end = 0.8, direction = 1) + xlab("")
save_plot("../manuscript/plots/h2_GR_site_weather_functions_All_Sites_k_specific.png", plot = grh2_p3, base_height = 3.5)

gr_fl_p1 <- plot_grid(grh2_p3, flh2_p3, nrow = 2)

>>>>

---
title: "Plots_manuscript_G_BLUP"
author: "Alice MacQueen"
date: "9/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Load data

Xiaoyu's annotation file, QTL 
```{r}
workingdir <- file.path("~", "Github", "pvdiv-phenology-gxe")
metadata <- read_rds(file.path(workingdir, "data", "metadata.rds"))
sites <- read_rds(file.path(workingdir, "data", "sites.rds"))
ftanno <- read_csv(file.path(workingdir, "data/Pvirgatum_v5.1.annotation_FTGeneHomologs.csv"))
```

# Create dataframes to plot (usually end with "_plot")

## QTL
```{r}
qtldf <- read_csv("~/Github/pvdiv-phenology-gxe/phenology-fourway/5-QTLmappingForAlice/QTLsWithFlankMarkers_FL50_phenotypes_Alice_7_SITES_Full_model.csv")
